Determining the alternatives for scalar implicature

### 2016-01-31 Paper/Paper.Rmd
shrunk literal listener plots to heigh=4

```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgments from Experiments 1a,b,c. Proportion of participants indicating compatibility (answering 'yes') is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Rows are grouped by scale and items within rows are ordered by valence. Colors indicate the specific experiment (1a,b,c) with experiments including different numbers of items."}

>>>>

```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgments from Experiments 1a,b,c. Proportion of participants indicating compatibility (answering 'yes') is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Rows are grouped by scale and items within rows are ordered by valence. Colors indicate the specific experiment (1a,b,c) with experiments including different numbers of items."}
